---
title: "nonlinearspikeslab"
output:
  md_document:
    variant: markdown_github
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**n.b.:** to update this file, you can change README.Rmd then run `make readme` in the command line.


# nonlinearspikeslab

<!-- badges: start -->
<!-- badges: end -->

<!--ts-->
<!--te-->

Spike and slab variable selection in nonlinear models

## Installation

Clone the repository to a local folder using a command like:


``` bash
git clone git@forgemia.inra.fr:konkam/nonlinearspikeslab.git
```

or in case the previous does not work:

``` bash
git clone https://forgemia.inra.fr/konkam/nonlinearspikeslab.git
```

Then: 

2) Open RStudio, open a new project inside the newly created folder

3) Press ctrl + maj + B

## Example 1: regression on the final size parameter

```{r}
library(nonlinearspikeslab)
library(nimble)
library(tidyverse)
```


```{r}
set.seed(0)
data = SimulateDataOneVariableParam(p=10)
data
```

### View simulated data

```{r}
PlotSimulatedData(data)
```

### Fit Spike and Slab model with fixed parameters



```{r}
mcmc_out = FitOneVariableParamSpikeAndSlab_fixed_sigmagamma(data, nu_0 = 10^(-4))
```
```{r}
posterior_on_number_of_covariates_selected(mcmc_out, warmup_prop = 0)
```

```{r, fig.height=20, fig.width=20}
traceplot(mcmc_out)
```
```{r}
posterior_predictive_estimate(data = data, mcmc_out = mcmc_out)
```

### Fit Spike and Slab model 


```{r}
mcmc_out = FitOneVariableParamSpikeAndSlab(data, nu_0 = 10^(-4))
```
```{r}
posterior_on_number_of_covariates_selected(mcmc_out, warmup_prop = 0)
```

```{r, fig.height=20, fig.width=20}
traceplot(mcmc_out)
```
```{r}
posterior_predictive_estimate(data = data, mcmc_out = mcmc_out)
```

### Prior posterior plot

```{r}
PriorPosteriorPlotScalarParams(mcmc_out, parnames = c("sigma", "Gamma", "omega", "alpha", "mu")) + scale_x_log10()
```

```{r}
PriorPosteriorPlotLargeVectorParams(mcmc_out, parnames = c("beta", "delta")) 
```

```{r}
PriorPosteriorPlotLargeVectorParams(mcmc_out, parnames = c("beta")) + scale_x_log10()
```

## Example 2: regression on the delay parameter, after reparametrisation

```{r}
set.seed(0)
data = SimulateDataOneVariableParam_reparam(beta = c(0.3, 0.3, 0.15, 0, 0, 0, 0, 0, 0), psi2 = 0.25, psi3 = 0.15, sigma = 1.)
data
```

### View simulated data

```{r}
PlotSimulatedData(data)
```
```{r}
mcmc_out = FitOneVariableParamSpikeAndSlabDelayReparam(data, nu_0 = 10^(-4), niter = 15000)
```
```{r}
posterior_on_number_of_covariates_selected(mcmc_out)
```

```{r, fig.height=20, fig.width=20}
traceplot(mcmc_out)
```
```{r}
posterior_predictive_estimate(data = data, mcmc_out = mcmc_out)
```
```{r}
PriorPosteriorPlotScalarParams(mcmc_out = mcmc_out, parnames = c("alpha", "sigma2", "psi1", "psi2", "psi3", "Gamma2"))
```

```{r}
PriorPosteriorPlotScalarParams(mcmc_out = mcmc_out, parnames = c("alpha", "sigma2", "psi1", "psi2", "psi3", "Gamma2")) + scale_x_log10()
```

